Navigating Hostility: The Effect of Nonprofit Transparency and Accountability on Donor Preferences in the Face of Shrinking Civic Space

### 2025-04-12 README.qmd
Update Quarto version in Docker
ope there's only one model

We use the [{renv} package](https://rstudio.github.io/renv/articles/renv.html) to create a stable version-specific library of R packages, and we use the [{targets} package](https://docs.ropensci.org/targets/index.html) to manage all the file dependencies and run the analysis. {targets} is especially helpful with long-running objects like the main models, which take ≈40 minutes to run—as long as upstream dependencies don't change, the models only need to run once, and can be loaded from {targets}'s data store thereafter.

@@

   - **Quarto 1.6.1** (or later). As of this writing, the current stable version of Quarto is 1.6.

>>>>

We use the [{renv} package](https://rstudio.github.io/renv/articles/renv.html) to create a stable version-specific library of R packages, and we use the [{targets} package](https://docs.ropensci.org/targets/index.html) to manage all the file dependencies and run the analysis. {targets} is especially helpful with long-running objects like the main model, which takes ≈40 minutes to run—as long as upstream dependencies don't change, the model only needs to run once, and can be loaded from {targets}'s data store thereafter.

@@

   - **Quarto 1.7.23** (or later). As of this writing, the current stable version of Quarto is 1.7.
